---
title: "Foundation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Subsetting Vector

What can you put in []?

1. Logical
2. Positive Integer
3. Negative Integer
4. Zero
5. Character
6. Nothing

`drop = FALSE` returns data.frame instead of matrix.

```{r}
x <- c(1.5, -2.3, 10, 9.3, 1.42, 0)

# 1. Logical: keep TRUEs
x[x > 4]

# 4. Zero: drops all
x[0]

# 6. Nothing gives you everything
x[]
mtcars[1:5, ]
mtcars[, c("vs", "am")]
```

## Object Size

`object.size` is not a reliable source of information. Use `pryr::object_size()` instead.

```{r}
x <- rnorm(1e6)
pryr::object_size(x)

y <- list(x, x, x)
pryr::object_size(y)
pryr::object_size(x, y)

# What if we change a value? R copies on modify.
y[[1]][[1]] <- 1
pryr::object_size(y)
```

## RStudio Shortcuts

#### Global

- `Alt + Shift + K` shows all keyboard shortcuts.
- `Cmd + Shift + F10` restart R session.

#### Console

- `Tab` autocompletes.
- `Cmd + Up Arrow` shows you command history.

#### Editor

- `Cmd + Enter` executes current line that the cursor is on.
